---
title: "ISLR: Chapter 3: Assignment"
author: "Akhilesh Jain"
date: "July 23, 2017"
output:
  html_document: default
  pdf_document: default
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=TRUE, warning=FALSE, message=FALSE)
```

## Load Libraries

```{r load library , results="hide"}
library("MASS")
library("ISLR")
```

Auto Dataframe

```{r summary , include=TRUE, echo=TRUE}
summary(Auto)
names(Auto)
attach(Auto) #Use column names as variables

#fix(Auto) # view dataframe
```

## Question 8

8. This question involves the use of simple linear regression on the Auto
data set.
(a) Use the lm() function to perform a simple linear regression with
mpg as the response and horsepower as the predictor. Use the
summary() function to print the results. Comment on the output.

```{r q8a , include=TRUE, echo=TRUE}
lm.fit=lm(mpg~horsepower,data=Auto)
summary(lm.fit)
confint (lm.fit) #confidence interval for the coefficients
```

i. Is there a relationship between the predictor and the response?

t-statistic>>1 indicates that the null-hypothesis is false and there is a relation ship between the predictor and response. A small p-value indicates that there is a small probability that this result is incorrect. 

ii. How strong is the relationship between the predictor and
the response?

The R^2 of the fit is 0.6059 indicating that 60% of the variance in mpg is explained by horsepower.

iii. Is the relationship between the predictor and the response
positive or negative?

The coefficient of horsepower is negative indicating that the relationship is negative.

iv. What is the predicted mpg associated with a horsepower of
98? What are the associated 95 % confidence and prediction
intervals?

```{r q8aiv , include=TRUE, echo=TRUE}
predict(lm.fit,data.frame(horsepower=98),interval="confidence")
predict(lm.fit,data.frame(horsepower=98),interval="prediction")
```


(b) Plot the response and the predictor. Use the abline() function
to display the least squares regression line.

```{r q8b , include=TRUE, echo=TRUE}
plot(horsepower,mpg)
abline(lm.fit,lwd=2,col="red")
```

(c) Use the plot() function to produce diagnostic plots of the least
squares regression fit. Comment on any problems you see with
the fit.

```{r q8c , include=TRUE, echo=TRUE}
par(mfrow=c(2,2))
plot(lm.fit)
```

## Question 9

9. This question involves the use of multiple linear regression on the
Auto data set.
(a) Produce a scatterplot matrix which includes all of the variables
in the data set.

```{r q9a , include=TRUE, echo=TRUE}
pairs(Auto, labels = colnames(Auto), main = "Auto Pairs matrix", pch = 21, 
      bg = c("red", "green3", "blue", "yellow", "green3", "red", "green3", "black")[unclass(Auto$cylinders)], lower.panel = NULL)
```

(b) Compute the matrix of correlations between the variables using
the function cor(). You will need to exclude the name variable, cor() which is qualitative.

```{r q9b , include=TRUE, echo=TRUE}
Auto2 = Auto[,(1:8)]
#head(Auto2)
COR <- cor(Auto2)
image(x=seq(nrow(COR)), y=seq(ncol(COR)), z=cor(Auto2), axes=F, xlab="", ylab="")
text(expand.grid(x=seq(dim(COR)[1]), y=seq(dim(COR)[2])), labels=round(c(COR),2))
box()
axis(1, at=seq(nrow(COR)), labels = rownames(COR), las=2)
axis(2, at=seq(ncol(COR)), labels = colnames(COR), las=1)
```

(c) Use the lm() function to perform a multiple linear regression
with mpg as the response and all other variables except name as
the predictors. Use the summary() function to print the results.
Comment on the output. For instance:
i. Is there a relationship between the predictors and the response?
ii. Which predictors appear to have a statistically significant
relationship to the response?
iii. What does the coefficient for the year variable suggest?

```{r q9c , include=TRUE, echo=TRUE}
lm.fit2=lm(mpg~.-name,data=Auto)
summary(lm.fit2)
```


(d) Use the plot() function to produce diagnostic plots of the linear
regression fit. Comment on any problems you see with the fit.
Do the residual plots suggest any unusually large outliers? Does
the leverage plot identify any observations with unusually high
leverage?
```{r q9d , include=TRUE, echo=TRUE}
par(mfrow=c(2,2))
plot(lm.fit2)
dev.off()
lev = hat(model.matrix(lm.fit2))
plot(lev)
Auto[lev>0.1,]
```

(e) Use the * and : symbols to fit linear regression models with
interaction effects. Do any interactions appear to be statistically
significant?
(f) Try a few different transformations of the variables, such as
log(X), √X, X2. Comment on your findings.