---
title: 'ISLR: Chapter 3 : Q12'
author: "Akhilesh Jain"
date: "July 31, 2017"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=8, fig.height=6, fig.path='Figs/',
                      echo=TRUE, warning=FALSE, message=FALSE)
```

12. This problem involves simple linear regression without an intercept.

(a) Recall that the coefficient estimate ˆ β for the linear regression of Y onto X without an intercept is given by (3.38). Under what circumstance is the coefficient estimate for the regression of X onto Y the same as the coefficient estimate for the regression of YontoX?

(i) When the sum of squares of x is same as sum of squares of y values.
(ii)the coefficient of x/y is 1

(b) Generate an example in R with n = 100 observations in which the coefficient estimate for the regression of X onto Y is different from the coefficient estimate for the regression of Y onto X.

####Linear regression with no intercept - different coefficients

```{r q11b , include=TRUE, echo=TRUE}
set.seed(1)
x=rnorm(100)
y=2*x+rnorm(100)
plot(x,y)
lm.fit=lm(y~x+0)
summary(lm.fit)
lm.fit2=lm(x~y+0)
summary(lm.fit2)
```


(c) Generate an example in R with n= 100 observations in which the coefficient estimate for the regression of X onto Y is the same as the coefficient estimate for the regression ofYontoX.

####Linear regression with no intercept - same coefficients

```{r q11c , include=TRUE, echo=TRUE}
set.seed(1)
x=rnorm(100)
y=-sample(x, 100)
plot(x,y)
lm.fit3=lm(y~x+0)
summary(lm.fit3)
lm.fit4=lm(x~y+0)
summary(lm.fit4)
```

We are sampling values from negative values x and assigning them to y such that sum of x^2 = y^2
