---
title: '"ISLR: Chapter 3 : Q11"'
author: "Akhilesh Jain"
date: "July 31, 2017"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=8, fig.height=6, fig.path='Figs/',
                      echo=TRUE, warning=FALSE, message=FALSE)
```

In this problem we will investigate the t-statistic for the null hypothesis H0 : β= 0 in simple linear regression without an intercept. To begin, we generate a predictor x and a response y as follows.

```{r dataset , include=TRUE, echo=TRUE}
set.seed(1)
x=rnorm(100)
y=2*x+rnorm(100)
plot(x,y)
```

(a) Perform a simple linear regression of y onto x, without an intercept. Report the coefficient estimate
ˆ β, the standard error of this coefficient estimate, and the t-statistic and p-value associated with the null hypothesis H0 : β= 0. Comment on these results. (You can perform regression without an intercept using the commandlm(y∼x+0).)

####Linear regression with no intercept (y on x)

```{r q11a , include=TRUE, echo=TRUE}
lm.fit=lm(y~x+0)
summary(lm.fit)
confint (lm.fit) #confidence interval for the coefficients
plot(x,y)
lines(x, lm.fit$fitted.values, type = "l", col = "red")
```

Coeffiecient: 1.9939
Standard error: 0.1065
t-val: 18.73
p-val:<2e-16

b) Now perform a simple linear regression ofxontoywithout an intercept, and report the coefficient estimate, its standard error, and the corresponding t-statistic and p-values associated with
the null hypothesisH0:β= 0. Comment on these results.

####Linear regression with no intercept (x on y)

```{r q11b , include=TRUE, echo=TRUE}
lm.fit2=lm(x~y+0)
summary(lm.fit2)
confint (lm.fit2) #confidence interval for the coefficients
plot(y,x)
lines(y, lm.fit2$fitted.values, type = "l", col = "red")
```

Coeffiecient: 0.39; Standard error: 0.02089; t-val: 18.73; p-val:<2e-16

(c) What is the relationship between the results obtained in (a) and (b)?

Models for predicting y & x. 

(d)

```{r q11d , include=TRUE, echo=TRUE}
(sqrt(length(x)-1) * sum(x*y)) / (sqrt(sum(x*x) * sum(y*y) - (sum(x*y))^2))
```

(e) Using the results from (d), argue that the t-statistic for the regression of y onto x is the same as the t-statistic for the regression of x onto y.

Swapping x for y gives the results. 

(f) In R, show that when regression is performed with an intercept, the t-statistic for H0: β1= 0 is the same for the regression of y onto x as it is for the regression ofx onto y.

```{r q11f , include=TRUE, echo=TRUE}
lm.fit3=lm(y~x)
summary(lm.fit3)
lm.fit3$coefficients
lm.fit4=lm(x~y)
summary(lm.fit4)
```
The t-value is same at 18.56

