---
title: "ISLR: Chapter 3: Q8 and 9"
title: "ISLR: Chapter 3 : Q8 & 9"
author: "Akhilesh Jain"
date: "July 23, 2017"
output:
  html_document: default
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=8, fig.height=6, fig.path='Figs/',
                      echo=TRUE, warning=FALSE, message=FALSE)
```

## Load Libraries

```{r load library , results="hide"}
library("MASS")
library("ISLR")
```

Auto Dataframe

```{r summary , include=TRUE, echo=TRUE}
summary(Auto)
names(Auto)
attach(Auto) #Use column names as variables

#fix(Auto) # view dataframe
```

## Question 8

8. Thise question involves the use of simple linear regression on the Auto
data set.
(a) Use the lm() function to perform a simple linear regression with
mpg as the response and horsepower as the predictor. Use the
summary() function to print the results. Comment on the output.

```{r q8a , include=TRUE, echo=TRUE}
lm.fit=lm(mpg~horsepower,data=Auto)
summary(lm.fit)
confint (lm.fit) #confidence interval for the coefficients
```

i. Is there a relationship between the predictor and the response?

t-statistic>>1 indicates that the null-hypothesis is false and there is a relation ship between the predictor and response. A small p-value indicates that there is a small probability that this association is statistically significant. 

(a small p-value indicates that it is unlikely to observe such a substantial association between the predictor
and the response due to chance, in the absence of any real association between the predictor and the response)

ii. How strong is the relationship between the predictor and the response?

The R^2 statistic of the fit is 0.6059 indicating that 60.59% of the variance in mpg is explained by horsepower.

iii. Is the relationship between the predictor and the response positive or negative?

The coefficient of horsepower is negative indicating that the relationship is negative.

iv. What is the predicted mpg associated with a horsepower of 98? What are the associated 95 % confidence and prediction intervals?

```{r q8aiv , include=TRUE, echo=TRUE}
predict(lm.fit,data.frame(horsepower=98),interval="confidence")
predict(lm.fit,data.frame(horsepower=98),interval="prediction")
```


(b) Plot the response and the predictor. Use the abline() function
to display the least squares regression line.

```{r q8b , include=TRUE, echo=TRUE}
plot(horsepower,mpg)
abline(lm.fit,lwd=2,col='red')
```

(c) Use the plot() function to produce diagnostic plots of the least
squares regression fit. Comment on any problems you see with
the fit.

```{r q8c , include=TRUE, echo=TRUE}
par(mfrow=c(2,2))
plot(lm.fit)
```

The leverage of an observation measures its ability to move the regression model all by
itself by simply moving in the y-direction. The leverage measures the amount by which
the predicted value would change if the observation was shifted one unit in the ydirection.

The leverage always takes values between 0 and 1. A point with zero leverage has no
effect on the regression model. If a point has leverage equal to 1 the line must follow the
point perfectly.

Plot of leverage of each point 

```{r q8 lev , include=TRUE, echo=TRUE}
lev = hat(model.matrix(lm.fit))
plot(lev)
Auto[lev>0.025,]
plot(horsepower,mpg, xlim=c(20,250), ylim=c(0,50))
par(new=TRUE)
plot(horsepower[lev>0.02],mpg[lev>0.02],col = 'red', xlab = "", ylab = "", xlim=c(20,250), ylim=c(0,50))
#points(Auto[7,]$horsepower,Auto[7,]$mpg, col = 'red')
```
The leverage for this case is pretty low at less than < 0.03. 

Prior to studying the residuals it is common to standardize them to compensate for differences in leverage. THe studentized residual are residuals normalized the leverage. Points with studentized residual > 3 are outliers.



```{r q8 residual , include=TRUE, echo=TRUE}
stud_residual = rstudent(lm.fit) # Calculate studentized results
plot(mpg,stud_residual)
```


An influential point is one if removed from the data would significantly change the fit. An
influential point may either be an outlier or have large leverage, or both, but it will tend
to have at least one of those properties. Cook’s distance is a commonly used influence
measure that combines these two properties. Points with Cooks distance greater than 1 are classified as being influential.


```{r q8 Cook dist , include=TRUE, echo=TRUE}
cookdist = cooks.distance(lm.fit) # Calculate Cook's distance
plot(cookdist,ylab="Cook's distance",col = 'blue', xlim=c(0,400), ylim=c(0,0.1))
```


## Question 9

9. This question involves the use of multiple linear regression on the
Auto data set.
(a) Produce a scatterplot matrix which includes all of the variables
in the data set.

```{r q9a , include=TRUE, echo=TRUE}
pairs(Auto, labels = colnames(Auto), main = "Auto Pairs matrix", pch = 21, 
      bg = c("red", "green3", "blue", "yellow", "green3", "red", "green3", "black")[unclass(Auto$cylinders)], lower.panel = NULL)
```

(b) Compute the matrix of correlations between the variables using
the function cor(). You will need to exclude the name variable, cor() which is qualitative.

####Correlation

```{r q9b , include=TRUE, echo=TRUE}
Auto2 = Auto[,(1:8)]
#head(Auto2)
COR <- cor(Auto2)
image(x=seq(nrow(COR)), y=seq(ncol(COR)), z=cor(Auto2), axes=F, xlab="", ylab="")
text(expand.grid(x=seq(dim(COR)[1]), y=seq(dim(COR)[2])), labels=round(c(COR),2))
box()
axis(1, at=seq(nrow(COR)), labels = rownames(COR), las=2)
axis(2, at=seq(ncol(COR)), labels = colnames(COR), las=1)
```

(c) Use the lm() function to perform a multiple linear regression
with mpg as the response and all other variables except name as
the predictors. Use the summary() function to print the results.
Comment on the output. For instance:
i. Is there a relationship between the predictors and the response?
ii. Which predictors appear to have a statistically significant
relationship to the response?
iii. What does the coefficient for the year variable suggest?

```{r q9c , include=TRUE, echo=TRUE}
lm.fit2=lm(mpg~.-name,data=Auto)
summary(lm.fit2)
```


(d) Use the plot() function to produce diagnostic plots of the linear
regression fit. Comment on any problems you see with the fit.
Do the residual plots suggest any unusually large outliers? Does
the leverage plot identify any observations with unusually high
leverage?
```{r q9d , include=TRUE, echo=TRUE}
par(mfrow=c(2,2))
plot(lm.fit2)
#dev.off()
```

```{r q9d lev , include=TRUE, echo=TRUE}
lev = hat(model.matrix(lm.fit2))
Auto[lev>0.1,]
plot(lev)
plot(horsepower,mpg, xlim=c(20,250), ylim=c(0,50))
par(new=TRUE)
plot(horsepower[lev>0.1],mpg[lev>0.1],col = 'red', xlab = "", ylab = "", xlim=c(20,250), ylim=c(0,50))
abline(lm.fit2,lwd=2,col='red')
```

(e) Use the * and : symbols to fit linear regression models with
interaction effects. Do any interactions appear to be statistically
significant?

```{r q9e , include=TRUE, echo=TRUE}
# lm.fit3=lm(mpg~.-name-cylinders-horsepower-acceleration-displacement,data=Auto)
# lm.fit3=lm(mpg~.-name-cylinders-horsepower-acceleration-displacement+origin*weight + origin*year +year*weight+displacement*weight+displacement*year,data=Auto)
lm.fit3=lm(mpg~.-name+origin*weight + origin*year +year*weight+displacement*weight+displacement*year,data=Auto)
summary(lm.fit3)
par(mfrow=c(2,2))
plot(lm.fit3)
```

Without interaction parameter, the most important predictors were:
displacement, weight, year and origin.

When taking into account interaction terms, the most significant predictors are:
horepower, year and displacement*weight


(f) Try a few different transformations of the variables, such as
log(X), √X, X2. Comment on your findings.

```{r q9f , include=TRUE, echo=TRUE}
lm.fit4=lm(mpg~.-name-displacement-cylinders+sqrt(weight)+sqrt(horsepower)+acceleration+I(acceleration^2),data=Auto)
summary(lm.fit4)
par(mfrow=c(2,2))
plot(lm.fit4)
```
Started out with log,sqrt and square of weight, hp and acceleration and eliminated the statistically insignificant variables. 

The most significant terms are sqrt(wt), sqrt(hp) and acc^2.
```{r q9f plot , include=TRUE, echo=TRUE}
# par(new=TRUE)

plot(horsepower,mpg)
# par(new=TRUE)
abline(lm.fit4,lwd=2,col='red')
```
